
Guidelines answered
\textbf{The Research Questions are as follows:}
\begin{enumerate}
	
	\item What are some privacy risks associated with traditional human localization systems in public spaces, and how may on-device processing mitigate these privacy concerns? 
	\item background and motivation
	\item individual privacy
	
	\item How does the validity of object detection model evaluations change when using data specifically from the intended deployment environment compared to using generic datasets?
	\item results and discussion
	
	\item What are some machine learning architectures suitable for object detection in a real-world deployment scenario?
	\item object detection, literature

	\item How many images are needed for testing before the average precision of a machine learning model converges in a single-environment setting?
	\item 
\end{enumerate}

\textbf{The Primary Objectives are to:}
\begin{enumerate}
	
	\item Develop a privacy-preserving human localization system using on-device processing to minimize data transmission and enhance data privacy.
	\item project
	
	\item Demonstrate feasability and effectiveness of on-device human detection and tracking in a practical and realistic setting.
	\item heatmaps and peak hours
	
	\item Investigate the effects of the dataset quality in fine-tuning of models on the performance.
	\item project
	
	\item Assess the impact of deployment-specific data on the accuracy and validity of object detection model evaluations, by comparing performance metrics with those obtained using generic datasets.
	\item project todo
\end{enumerate}

\textbf{The Secondary Objectives are to:}
\begin{enumerate}
	
	\item Compare the privacy and performance impacts of on-device processing against traditional centralized methods.
	\item visitor behaviour analysis
	
	\item Investigate the feasibility of deploying the developed system in public spaces to enhance visitor analytics and security.
	\item visitor behaviour analysis
	
	\item Demonstate how to visualize object detection data by creating visualizations of collected data from a realistic setting.
	\item project
	
	\item Explore relevant object detection architectures to evaluate their performance in a real-world deployment sceneario.
	\item project 
\end{enumerate}

\newpage
\subsubsection{Action Points}
\label{sec:action_points}
\textbf{In order to achieve these objectives, the candidate shall:}
\begin{itemize}
    
	\item Design and implement a prototype system that incorporates on-device processing for privacy-preserving human localization.
    
	\item Deploy the prototype in a controlled environment to gather real-world data and analyze system performance.
    
	\item Conduct comparative studies using different datasets to understand the effects of data specificity and quality on model accuracy.
    
	\item Perform a comparative analysis of various object detection architectures under real-world conditions to identify optimal configurations for specific deployment scenarios.
    
	\item Develop and utilize data visualization tools to represent data findings in a way that facilitates clear understanding and decision-making.
\end{itemize