\subsubsection*{Study objectives} revisited
\begin{enumerate}
    \item A comparative analysis of distinct machine learning models fit for edge computation in embedded systems in the task of human detection.
    \item A comparison of the maximum throughputs of the YOLO (v3) machine learning model when executed on two specific single-board computer models, i.e. Raspberry PI 3, Jetson Nano, and Rock (Pi) 4 SE. \footnote{These are the available hardware for the study, as well as being widely used in research and industry}.
    \item A comparison of the aforementioned models ability to extract accurate positional data of all people within each image, considering factors like pose, orientation, varying lights and occlusion (which all are highly relevant in a museum setting).
    \item A system architecture description that allows for a throughput of at least 15 image to be processed per hour (4 min/per image).
    \item Investigate and address challenges associated with deploying machine learning models on embedded systems. Analyze how these limitations may impact the choice of algorithms for a given use case.
\end{enumerate}

NOTATER OM OBJEKTIVENE:
4.. for a selected create an implementation of selected models where the achieved ouput is at least 12. Hvilken metode med hvilken maskinvare? Må koble sammen med noe annet?

5- Devices in general.

6. hva er mer cost-effective og hva er higher-end alternatives?

7. skulle denne vært før throughtput... 
"the model", da høres det ut som at vi har valgt ut et 
ag skisse, hvilke modeller jobber vi med hvor, hva e rbudskapet?

8. her er det system og ikke modell, hvilket suystem er det snakk om her? 

snakker om 3 system eksempler med enkel algoritme på hardware. 

målsetningen er å finne metoder som er gode for dette. Hva er the most 

Identify and rank the most caoabale models...
based on limitatios of availablility ... om rock eller pi 3. 

in order to do this...
the candidate shall

secondary objectives. 

Dette er en gjøreliste, ikke måsetning
Hva er mine objective,s hv
Ikke gjøremål, men at det er hva er outcome, primary objectives, ikke hva som skal 

In order to achieve these objectives, the 
limitations i introduksjonen, her vil prosjektet bli limited to.... so the primary work will consist of ....
Hva er det vi egentlig vil oppnå

Det å ytnutte egenskaper i et problem gjør produktet mer spesialisert for den oppgaven. For å gjøre produktet generelt må man la være å utnytte egenskapene i problemet.